---
title       : Dog Age Calculator App
subtitle    : Developing Data Products Course Project
author      : Azul Celeste
job         : 
framework   : io2012   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Summary

This application has been created as a course project of the Developing Data Products course.

Have you ever asked yourselve how old your dog is? Well, you found to the right App...

* The Shiny App calculates the age and seniority of a dog based on its age in human years
* User must submit in the App the age and size of the dog.
* The application determines the age in Dog years and returns how old is your dog: puppy, young adult, middle age or senior.


--- .class #id 

## Building the App

Basic inputs were used to collect data as you can see in the section below

```{r message = FALSE, eval=FALSE} 
library(shiny)

shinyUI(
   pageWithSidebar(
     #Application Title
        headerPanel("Dog Age Calculator"),
        sidebarPanel(
                selectInput('humanAge', 'Age in Human Years', choices = ageOptions),
                radioButtons('dogSize', "Choose the size of your dog", choices = sizes),
                submitButton('Submit')
        ),

```


--- .class #id 

## Inputs
```{r echo = FALSE}
#inputs data for dog age 
#from The Dog Owner's Manual published by QUIRK BOOKS
ageOptions <- c(0.5, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14)
SM <- c(10, 16, 24, 29, 34, 39, 44, 49, 54, 59, 64, 69, 74, 79, 84)
L <- c(10, 16, 24, 30, 36, 42, 48, 54, 60, 66, 72, 78, 84, 90, 96)
G <- c(10, 16, 24, 31, 38, 45, 52, 59, 66, 73, 80, 87, 94, 101, 108)

```
The inputs for the App are contained in a global file. Let's see how the age of the dog depends as a function of the dog size:

```{r echo=TRUE, fig.width = 4, fig.height = 4}
plot(SM, ageOptions,type = "l", col ="blue", xlab = "Age of Dog in Human Years", 
     ylab = "Age in Dog years", main = "Dog Age vs Size" )
lines(L,ageOptions, col = "red")
lines(G,ageOptions, col = "green")
legend("topleft", c("Small/Medium", "Large", "Giant"), text.col=c("blue", "red", "green"))
```


--- .class #id 

## Supporting Resources

More information on the Developing Data Products course project can be found here:
https://www.coursera.org/course/devdataprod

For more information about RStudio Shinyapps.io visit:
http://shiny.rstudio.com/articles/shinyapps.html




